\documentclass[fleqn, 12pt]{exam}
\usepackage[font=small,format=plain,label font=bf,up, textfont=it,up]{caption} %
\usepackage[utf8]{inputenc}      % permits smartquotes, accents, etc. UTF8
\usepackage{amsfonts} %
\usepackage{amsmath} %
\usepackage{pgf,tikz}
\usepackage{pgfplots}
\usepackage{array, dcolumn} %
\usepackage{booktabs} %
\usepackage{fullpage} %
\usepackage{geometry} \geometry{letterpaper}           % See geometry.pdf for layout options.
\usepackage{graphicx} %
\usepackage{longtable} %
\usepackage{mathtools} %
\usepackage{microtype} %% suppress ligatures %
\usepackage{rotating} %
\usepackage{setspace} %
\usepackage{tabularx} %
\usepackage{titling} %
\usepackage{multicol} %
\usepackage{url} %
\usepackage{verbatim} %
\usepackage[round]{natbib} %%
\usepackage{bibentry} %%
\bibliographystyle{plainnat}
\nobibliography*
\usepackage{hyperref} %
\hypersetup{pdfcreator = {LaTeX with hyperref package}, %
  pdfproducer = {pdflatex},%
  pdfpagelabels,%
  hidelinks=true,%
  plainpages=false,%
  colorlinks=false,%
  citecolor=black,%
  filecolor=black,%
  linkcolor=black,%
  urlcolor=black%,
  pdfauthor = {Michael Ash},%
  pdftitle={Corporate Toxics Information Project}, %
  pdfsubject={Corporate Toxics Information Project}, %
  pdfkeywords={Corporate Toxics Information Project} }

\title{Corporate Toxics Information Project}
\author{Michael Ash\thanks{Department of Economics, School of Public Policy, Political Economy Research Institute, University of Massachusetts Amherst, \href{mailto:mash@umass.edu}{\tt mash@umass.edu}}}
\date{\today}

\begin{document}
\maketitle
\thispagestyle{empty}

\begin{center}
  \fbox{\fbox{\parbox{6in}{
        Scavenger hunt and directions for session. Introduction to the Corporate Toxics Information Project \url{http://toxic100.org}. 
      }  }}
\end{center}

\begin{questions}

  \question Visit the Air Toxics at School interactive tool. Request a report on a school that you have attended. What are the Top 5 chemicals by risk from industrial point source releases (US EPA Toxics Release Inventory)? What facilities are the sources for these releases?  Where does the school rank among schools in the same state and among all schools in U.S.?  Is it easy or possible to ascertain an absolute risk level, for example, increase in cancer risk at the school location?

  \question Visit the Top 100 Polluter Indexes.  Find a publicly traded company that appears on the Toxic 100 Air Polluters Index, the Toxic 100 Water Polluters Index, the Greenhouse 100 Index, and the Greenhouse Suppliers 100 Index. Find a privately held company that appears on the Toxic 100 Air Polluters Index, the Toxic 100 Water Polluters Index, the Greenhouse 100 Index, and the Greenhouse Suppliers 100 Index.

  \question Visit the Toxic 100 Air Polluters listing for two oil companies.  For each company, find a facility that has both a high Toxic Score and a high EJ: Minority Share.  (What does Toxic Score measure?  What does EJ: Minority Share measure?)

    
  \question What is the difference between the Greenhouse Suppliers 100 Index and the Greenhouse 100 Index?  What type of company dominates the top of the Greenhouse Suppliers 100 Index?  What type of company dominates the top of the Greenhouse 100 Index?

  \question Visit the Coal Producers \& Greenhouse Gas Emissions Index.  Identify a coal producer that interests you from the standpoint of just transition. 

  \question Which of the 100 lists shows the highest \emph{disproportionality} (the highest share of the total for all 100 accounted for by the top 2, 5, or 10 facilities)?


    
    
    

\end{questions}




\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
